Time Series Bootstrapping For Solar Current

### 2021-12-17 deliverables/paper.Rmd
Fixed grammar errors, added detail

This project began with the search for a research paper
utilizing the process of Monte Carlo sampling or other 
statistcal computing methods. We landed on a few papers 
that did exatcly this, one titled, "SolarStat: Modeling 
Photovoltaic Sources through Stochastic Markov Processes". 
Instead of comparing our works of Monte Carlo simulations 
we were able to utilize a more recent topic discussed in class.
This of course was bootsrapping, a topic we didn't get too in
depth about; however, everything needed to know will be explained 
later on in the paper. Regarding our choice of articles, it was a
question of interest and importance. During the last decade the world
has seen a massive uptick in renewable energy pushes. With this 
new wave of renewables and the rather large misunderstanding of their
total power we decided it would be interesting to look into solar and 
what it was all about. The big question being asked regarding
solar power is whether or not it is worth heading the initial cost
of set up and general mantienance. Many websites inform users of 
just this, according to the Solar.com Learning Center, the average
solar panel net cost is \$2,700 per 1.5 kilowatt-hour system (@solar.com). 
The biggest upside to solar panels is being able to slice down your 
energy bill, and eventually have it pay for itself. In order to 
calculate a solar panels net output experts recommend looking at three things:

@@

To translate raw irradiance data into meaningful power data, several steps
had to be taken to simulate the electrical workings of a real PV module. First,
adjustments had to be made to account for the fact that an imperfect amount of
irradiance actually reaches a PV module for capture. Then, effective irradiance
must be translated into output current and maximized with an attached power
processor. The process and accompanying assumptions are given below.

## Effective Irradiance

@@

## PV Module

@@

@@

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost per kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. As stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. As a disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we decided to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of \$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning \$`r round(round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW),2)` yearly on one solar panel grid. 
Knowing this, any resident located in or around the Los Angeles area should
feel confident in their decision of purchasing a solar panel grid.

The power estimate generated in this study has practical applications 
in real-world electrical engineering problems. An allocation must be 
made that balances the expected contribution of renewable energy 
sources with the expected residual demand on the electrical grid. 
An intelligent estimate of the contribution from PV modules must account 
for geographical deviations in solar irradiance. While the estimate here 
was made for Los Angeles, this framework can be applied to any location 
for which irradiance data is tracked. This framework could also be applied to 
intervals of time where power estimates could be made for each hour of the 
day or for each day of the year; greater stratified specificity would 
improve the real-world usefulness of this method.

In regard to consumer usage, an automated website could be created 
related to the information received in this paper. A simple 
user input of location could pull all the values necessary to caluclate
a predicied solar irradiance and transform that 
information, as we did above, into an estimate of total yearly 
solar panel energy cost return. This may not even just be important 
information to jsut consumers, considering the push of renewable energy 
research in the last few years by the US governement, this could be used
to find the best areas in the US to began creating large-scale solar plants. 
Finding the best city throughout the US in which NREL holds data on would turn 
our problem into an optimization one.

For future work, it would be good to examine the wider implications
of the inferential results explored in this paper.
The model paper for this project simulated results for small solar panels
in a specific configuration,
making it hard to generalize the results to any meaningful solar array.
However, if the results could be generalized,
it would be good to see how power output based on solar irradiance
fits into a larger model of uncertainty surrounding renewable energy generation.
One example of such an approach would be @constante_2018,
in which PV output simulated from solar irradiance
is used in conjunction with other sources of of uncertainty.
The estimates of PV output in this paper are only part
of the story with respect to uncertainty in PV power generation.
Other relevant types of uncertainty are uncertainty of energy demand,
uncertainty in personal PV module placement on the grid,
and uncertainty in the power generation of other renewable energy
sources, to name a few (@constante_2018).

>>>>

This project began with the search for a research paper
utilizing the process of Monte Carlo sampling or other 
statistical computing methods. We landed on a few papers 
that did exactly this, titled "SolarStat: Modeling 
Photovoltaic Sources through Stochastic Markov Processes"
(@miozzo_2014). 
The paper's objectives were to simulate power output from
a small grid of solar panels in Los Angeles using solar radiance data,
and then cluster those results into different levels
of radiance using Markov models.
We adapted this approach.
The goal of this paper was to use the power output
simulation model from @miozzo_2014 to obtain similar
power output results,
and then to apply and compare two types of bootstrapping estimates,
resulting in an overall estimate of power output.
The two types of bootstrapping estimates
are an *iid* bootstrap, which assumes the data is independent,
and a block bootstrap, which assumes dependence in the data.
We wanted to see in what ways these methods produced differing
results, and hopefully obtain an accurate estimate of energy output.

This problem is relevant to current trends in energy:
During the last decade the world
has seen a massive uptick in renewable energy pushes. 
The big question being asked regarding
solar power is whether or not it is worth heading the initial cost
of set up and general maintenance. Many websites inform users of 
just this, according to the Solar.com Learning Center, the average
solar panel net cost is \$2,700 per 1.5 kilowatt-hour system (@solar.com). 
The biggest upside to solar panels is being able to slice down your 
energy bill, and eventually have it pay for itself. In order to 
calculate a solar panels net output experts recommend looking at three things:

@@

To translate raw irradiance data into meaningful power data, several steps
had to be taken to simulate the electrical workings of a real PV (photovoltaic)
module. First,
adjustments had to be made to account for the fact that an imperfect amount of
irradiance actually reaches a PV module for capture. Then, effective irradiance
must be translated into output current and maximized with an attached power
processor. The process and accompanying assumptions are given below.

Note that, for all physical parameters given,
@miozzo_2014 relied on the physical characteristics
of a Solarbotics SCC-3733 Monocrystalline micro-solar panel
[@miozzo_2014, p. 691].
This means that all power output results should be
weighed against this model panel.

### Effective Irradiance

@@

### PV Module

@@

We assumed that based on the nature of solar data,
the data would contain almost 50\% structural zeros,
corresponding to nighttime hours.
We decided that, after transforming GHI to power output,
we would filter out the structural zeros
based on the distribution of the output data,
before analysis.

This would provide a more accurate assessment of power
output than simply averaging over a 24-hour period,
in which many of the hours would have zero power output
by nature of the day-night cycle.

@@

These estimates provide consumers with an answer to 
a very pressing question. As discussed in the introduction, one of the biggest 
problems about purchasing a solar panel is whether or not 
it will end up paying for itself. One of the three stipulations in 
order to calculate your average yearly return is a solar 
panels output. After using bootstrapping we were able to 
calculate a solar panel in Los Angeles' production 
output being `r round(power_out_est_year/1000)`. Now, all 
that is needed is the peak hours and total average cost per kWh. 
The former can be calculated by setting a lower floor on 
solar irradiance. As stated on Solar Reviews, 
"1 peak sun hour" is equal to, "1000 W/m² of sunlight 
per hour" (@energysage). In our calculations we used an hour window between 
8am to 4pm, a typical day range where the sun is overhead. As a disclaimer,
some of the values at the beginning and end of the day may not hold 
exactly greater than our cutoff stated by Solar Reviews, however this range 
yielded the greatest results of solar irradiance and Wh, some being much larger
than 1000 W/m^2 and others being just under. Therefore, we decided to use 
this range as our peak hours. Taking this total of `r length(HOUR_WINDOW)` 
peak hours and our average cost per kilowatt-hour of \$0.03 from before 
we would find that on average a consumer in Los Angeles can 
anticipate earning \$`r round(round(power_out_est_year/1000,2)*.03*length(HOUR_WINDOW),2)` yearly on one solar panel grid. 
It is unclear how these results would scale with a solar panel
or solar grid using different components.
Our simulation was based on physical parameters provided
in @miozzo_2014,
which in turn only estimate the characteristics of
the model solar panel.
Furthermore, the model solar panel was a "micro-solar" panel:
the 6x6 grid of panels had a reported size of
26.96 cm$^2$, according to @miozzo_2014 [@miozzo_2014, p. 695].
A larger or more efficient panel may be able to generate more
total power,
meaning that it may be possible for a consumer to purchase
a larger solar panel with more output.

The power estimate generated in this study has practical applications 
in real-world electrical engineering problems.
In real-world power grids,
the expected contribution of renewable energy 
sources 
is balanced
with the expected residual demand on the electrical grid. 
An intelligent estimate of the contribution from PV modules must account 
for geographical deviations in solar irradiance. While the estimate here 
was made for Los Angeles, this framework can be applied to any location 
for which irradiance data is tracked. This framework could also be applied to 
intervals of time where power estimates could be made for each hour of the 
day or for each day of the year; greater stratified specificity would 
improve the real-world usefulness of this method.

In regard to consumer usage, an automated website could be created 
related to the information received in this paper. A simple 
user input of location could pull all the values necessary to calculate
a predicted solar irradiance and transform that 
information, as we did above, into an estimate of total yearly 
solar panel energy cost return. This may not even just be important 
information to just consumers, considering the push of renewable energy 
research in the last few years by the US government, this could be used
to find the best areas in the US to began creating large-scale solar plants. 
Finding the best city throughout the US in which NREL collects data 
would allow power output to be optimized by location,
as it likely is in practice.

For future work, it would be good to examine the wider implications
of the inferential results explored in this paper.
As mentioned,
the model paper for this project, @miozzo_2014, simulated
results for small solar panels
in a specific configuration.
This makes it hard to generalize the results to any meaningful solar array.
However, if the results could be generalized,
it would be useful to see how power output based on solar irradiance
fits into a larger model of uncertainty surrounding renewable energy generation.
One example of such an approach would be @constante_2018,
in which PV output simulated from solar irradiance
is used in conjunction with other sources of of uncertainty.
The estimates of PV output in this paper are only part
of the story with respect to uncertainty in PV power generation.
Other relevant types of uncertainty are uncertainty of energy demand,
uncertainty in personal PV module placement on the grid,
and uncertainty in the power generation of other renewable energy
sources, to name a few (@constante_2018).
